The transition redshift as a probe of reionization

### 2019-08-14 paper/ms.tex
Update ms.tex

The number of modes is given by,
\beq \label{eq:nmodes}
N_m = \frac{4\pi k^2 \delta k}{V_{\text{fund}}}\text{,}
\eeq
where $\delta k$ is the width of the $k$-bin and $V_{\text{fund}}$ is the
volume of a fundamental mode. We assume a square survey area, and so this is
given by,
\beq \label{eq:fund}
V_{\text{fund}} = \frac{(2 \pi)^3}{L_{\perp}^2 L_{\parallel}}\text{,}
\eeq
where $L_{\perp}$ is the  and $L_{\parallel}$ is the comoving
length of the redshift extent of the bin. The optimal redshift binning is not
entirely clear, since the observational target is not the power spectrum. We
assume a redshift bin of $\Delta z = 0.03$, which is smaller than the expected
error we compute on \zst{}, and so is not an unreasonable choice.

We assume a $k$-bin of fairly large width, from $k=0.1$ to $0.3\,\Mpc^{-1}$.

By expanding $P_{21,i}$ as a linear function about \zst{}, we can estimate the
error on \zst{} by
\beq \label{eq:error_on_zst}
\Var{\zst} = \left(\left.\frac{\partial P_{21,i}}{\partial z}\right|_{\zst}\right)^{-2} \Var{P_{21,i}}
\eeq

>>>>

The number of modes is given by,
\beq \label{eq:nmodes}
N_m = \frac{4\pi k^2 \delta k}{V_{\text{fund}}}\text{,}
\eeq
where $\delta k$ is the width of the $k$-bin and $V_{\text{fund}}$ is the
volume of a fundamental mode. We assume a square survey area, and so this is
given by,
\beq \label{eq:fund}
V_{\text{fund}} = \frac{(2 \pi)^3}{L_{\perp}^2 L_{\parallel}}\text{,}
\eeq
where $L_{\perp}$ is the  and $L_{\parallel}$ is the comoving length of the
redshift extent of the bin. The optimal redshift binning is not entirely
clear, since the observational target is not the power spectrum. We assume a
redshift bin of $\Delta z = 0.03$, which is smaller than the expected error we
compute on \zst{}, and so is not an unreasonable choice. We assume a $k$-bin
of fairly large width, from $k=0.1$ to $0.4\,\Mpc^{-1}$.

By expanding $P_{21,\Ha}$ as a linear function about \zst{}, we can estimate the
error on \zst{} by
\beq \label{eq:error_on_zst}
\Var{\zst} = \left(\left.\frac{\partial P_{21,\Ha}}{\partial z}\right|_{\zst}\right)^{-2} \Var{P_{21,\Ha}}\text{,}
\eeq
where ${\partial P_{21,\Ha}}/{\partial z}$ is computed numerically.
